Argennon: A Scalable Smart Contract Platform

### 2021-06-03 tex/sections/avm.tex
Add the pronunciation note
Signed-off-by: aybehrouz <behrouz_ayati@yahoo.com>
Fix a few typos
Signed-off-by: aybehrouz <behrouz_ayati@yahoo.com>

The Argennon Virtual Machine (AVM) is an abstract computing machine for executing Argennon's smart contracts. The
Argennon Virtual Machine knows nothing of the Argennon blockchain, only of Argennon's identifier tries and
the concept of execution sessions.

@@

\begin{itemize}
    \item \texttt{alloc}: creates a new memory chunk of the specifies size in the heap. the identifier
    of the new chunk will be the concatenation of the \texttt{applicationID} of the creator of the chunk and
    the \texttt{id} operand. The specified identifier must be concatenation of
    an \texttt{accountID} and a prefix code
    generated by the \emph{local} prefix tree: \texttt{id = accountID|localID}. If the identifier is not valid or
    if it already exists in the heap a catchable exception will be thrown.

    \item \texttt{delete}: deletes the chunk that its identifier is the concatenation of the current smart
    contract \texttt{applicationID} to the specified \texttt{id}. If the identifier is not valid or
    if the chunk was not found a catchable exception will be thrown.
\end{itemize}

When a smart contract allocates a new memory chunk, the identifier of the new chunk is not generated by
the AVM, instead the smart contract can choose an identifier itself. This is a very important feature of
the AVM heap which allows smart contracts to use the AVM heap as a dictionary (map) data structure.
Because the \texttt{chunkID} is a prefix code, any smart contract has its own identifier space and a smart contract
can easily generate unique identifiers for its chunks.

The AVM requires the chosen identifier to be a prefix code made by concatenating a code compatible with
the \emph{accounts} prefix tree to a code compatible with the \emph{local} prefix tree. This requirement will
enable AVM to detect invalid identifiers while smart contracts can easily associate data with account identifiers.
At the same time, A smart contract is able to create maps with costume keys by appending local identifiers
to the \texttt{accountID} zero, which does not correspond to a valid account in the Argennon.

>>>>

The Argennon\footnote{the classical pronunciation should be used:\textipa{/ar"gen.non/}} Virtual Machine (AVM) is an
abstract computing machine for executing Argennon's smart contracts. The
Argennon Virtual Machine knows nothing of the Argennon blockchain, only of Argennon's identifier tries and
the concept of execution sessions.

@@

\begin{itemize}
    \item \texttt{alloc}: creates a new memory chunk of the specified size in the heap. the identifier
    of the new chunk will be the concatenation of the \texttt{applicationID} of the creator of the chunk and
    the \texttt{id} operand of the instruction. The \texttt{id} operand must be the concatenation of
    an \texttt{accountID} and a prefix code
    generated by the \emph{local} prefix tree: \texttt{id = accountID|localID}. If the identifier is not valid or
    if it already exists in the heap a catchable exception will be thrown.

    \item \texttt{delete}: deletes the chunk that its identifier is the concatenation of the current smart
    contract \texttt{applicationID} and the specified \texttt{id} operand. If the identifier is not valid or
    if the chunk was not found a catchable exception will be thrown.
\end{itemize}

When a smart contract allocates a new memory chunk, the identifier of the new chunk is not generated by
the AVM, instead the smart contract can choose an identifier itself. This is a very important feature of
the AVM heap, which allows smart contracts to use the AVM heap as a dictionary (map) data structure.
Since the \texttt{chunkID} is a prefix code, any smart contract has its own identifier space and a smart contract
can easily generate unique identifiers for its chunks.

The AVM requires the chosen identifier to be a prefix code made by concatenating a code compatible with
the \emph{accounts} prefix tree to a code compatible with the \emph{local} prefix tree. This requirement
enables AVM to detect invalid identifiers, while smart contracts can easily associate data with account identifiers.
At the same time, A smart contract is able to create maps with costume keys by appending local identifiers
to the zero \texttt{accountID}. Zero \texttt{accountID} does not correspond to a valid account in the Argennon
blockchain.
